Formalizing the Edmonds-Karp Algorithm

### 2016-03-01 paper/root.tex
Adjusted runtime difference in abstract
Finished Fofu formalization section

We then use stepwise refinement to obtain the Edmonds-Karp algorithm and prove its upper complexity bound of $O(|V||E|^2)$.
Further refinement yields a verified implementation, which is only 2.5 times slower than an unverified  
reference implementation in Java.

@@

\Snippet{isar-lem}

>>>>

We then use stepwise refinement to obtain the Edmonds-Karp algorithm and prove its upper complexity bound of $O(|V||E|^2)$.
Further refinement yields a verified implementation, which is almost as fast as an unverified  
reference implementation in Java.

@@

A formal proof contains many technical details that are not presented in an informal proof. While dealing with the technical details in a proof causes distraction, leaving out such details makes it hard to follow the proofs. Our formal proof of the Ford-Fulkerson method closely follows the informal proof described by Cormen et al. [cite]. So, readers may use this informal proof as a guide to better understand the relevant thoughts in our formal proof. Moreover using the proof language Isar, we made the formal proof readable even for readers that are not familiar with Isabelle.

As an example consider the following formal proof. Let $cf$ be the residual graph corresponding to a flow $f$ in an $s$-$t$ network $c$, and let $f'$ be a flow in $cf$. Consider the definition of the augment function that was described in previous section. The following lemma states that the result of augmenting $f$ with $f'$ is another function which satisfies the capacity constraint of a $s$-$t$ flow in $c$. 
\Snippet{isar-lem}

Most of the reference books in the field of algorithm provide pseudocodes instead of executable implementations. However, implementing an abstract presentation of 
an algorithm involves many technical details that are never presented in the books. We also tried to fill in this gap. First, we present the Ford-Fulkerson method using the syntax of Autoref[cite] tool which is quite similar to pseudocode of the algorithm. Next, we refine the abstract representation into an executable implementation. For instance, the following Isabelel definition abstractly presents the Ford-Fulkerson method.
\Snippet{6.1-1_0}
\Snippet{6.1-1}
